Towards a computational framework using finite element methods with Arbitrary Lagrangian-Eulerian approach for swimmers with contact

### 2024-08-13 article.swimmer-framework-contact.springer.tex
edit tex + add bibtex

\title*{Towards a computational framework using finite element methods with Arbitrary Lagrangian-Eulerian approach for swimmers with contact}
\titlerunning{\review{A computational framework for swimmers}}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Luca Berti, Laetitia Giraldi, Christophe Prud'homme, Céline Van Landeghem}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Luca Berti \at CNRS - Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg  \email{berti@math.unistra.fr}
\and Laetitia Giraldi \at Universit\'e C\^ote d'Azur, INRIA, CNRS, Calisto team, \email{laetitia.giraldi@inria.fr}
\and Christophe Prud'homme \at Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg - CNRS \email{christophe.prudhomme@math.unistra.fr}
\and Céline Van Landeghem \at Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg - CNRS \email{c.vanlandeghem@unistra.fr}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract{Swimming involves a body's capability to navigate through a fluid by undergoing self-deformations. Typically, fluid dynamics are described by the Navier-Stokes equations, and when integrated with a swimming body, it results in a highly intricate model. This paper introduces a computational framework for simulating the movement of multiple swimmers with various geometries immersed in a Navier-Stokes fluid. The approach relies on the finite element method with an Arbitrary Lagrangian-Eulerian (ALE) framework to handle swimmer displacements. Numerous numerical experiments demonstrate the adaptability of the computational framework across various scenarios.
All the implementations are made using the \feelpp\ finite element library \cite{feelpp-ref}.}

@@

The problem of simulating the motion of deformable swimmers in a fluid can be addressed through various approaches, depending on the flow regime. In the low Reynolds number limit, when the viscous effects prevail over inertial effects, as it is the case for microscopic bodies in very viscous fluids \cite{Purcell77}, it is legitimate to consider that the fluid is governed by the Stokes equations \cite{BrennerHappel65,PowersLauga09}.

@@

In this case, the hydrodynamic drag can be simplified asymptotically by employing the Resistive Force Theory \cite{GrayHanccok}, in which the hydrodynamic friction is related to the fluid velocity via an %prescribed 
anisotropic relation %operator 
depending on some parameters that account for the shape of the moving object. This approach does not require the numerical solution of the Stokes equations, but it has a
%Nevertheless, these approximations have 
very limited physical validity, often restricted to the case of very simple boundary-free domains.

%SBT
Slender body theory improves the Resistive Force Theory
to investigate the dynamics of slender particles in highly viscous flows \cite{cox1970motion, batchelor1970slender, keller1976slender,johnson1980improved}. 
This approach involves solving an integral equation which describes the effects of the fluid on the slender body. Assuming small deformations, the equilibrium of forces and torques can be expressed as a partial differential equation \cite{Gadhela_2013,  Clement_2018, Zakarya_2022}, whose solution defines the curve that describes the fiber. However, this method neglects the effects of fiber deformation on the fluid, leading to an approximation in accounting for the effects of the displacement of multiple swimmers.

%BEM (Lefebvre - Maury - Kenta)
A numerical method that is widely used in the micro-swimming community is the boundary element method, that relies on the integral formulation of the Stokes equations to determine the fluid velocity field \cite{pozrikidis1992boundary}. 
This formulation reduces the \review{computational} cost of the dynamics of the swimmer by working on the swimmer's boundary alone, which ensures significant memory savings since the fluid domain is not discretized. 
The boundary integral formulation expresses the fluid velocity at the boundary of the swimmer as a function of fluid stresses and velocities, via the fundamental solutions of the Stokes equations. Since these functions exhibit singular behaviour when the source and evaluation points are close together, a regularisation procedure needs to be employed for the numerical solution. Several solutions are possible: a regularisation of the numerical approximation of the singular integrals using a semi-analytic procedure \cite{huang_cruse} or the use of regularised kernels \cite{Fauci}.

@@

% Méthode de frontière immergée
When inertial effects become more important and the low Reynolds number assumption is no longer valid, 
it is necessary to resort to the solution of the system coupling Navier-Stokes equations with Newton's equations for rigid bodies. 
A commonly used method involves approximating the values of fluid velocity and pressure on a fixed discretization of the domain and representing the swimmers using an implicit function that parameterizes their boundaries. 
These approaches are commonly referred \review{to as} Immersed Boundary Methods with level set functions describing the swimmer. 
The challenge of these methods lies in following the swimmer. 
For instance, one may use methods called CutFEM (Cut Finite Element Method), which project the swimmer's boundary onto the fixed mesh \cite{Monasse,Iollo,bergmann2016bioinspired,hansbo2016cut,burman2015cutfem}.
%\review{However, this approach is computationally costly.}
%the CUTFEM approach in which mesh intersections are computationally costly.

@@

% Méthode FEM-ALE
In this chapter, we discuss an alternative method to compute the displacement of multiple deformable swimmers immersed in a Navier-Stokes fluid, which can be confined within a geometrically complex domain. This method is based on the finite element solution of the swimming problem, using the Arbitrary-Lagrangian-Eulerian description for the motion of the fluid domain.
This approach is popular in fluid-structure interaction problems \cite{chabannes2013high,pena2012high}, and it is based on a formulation of the fluid equations in an intermediate frame between the Eulerian and Lagrangian description.
A characteristic of this method is that the solutions are approximated on a mesh that deforms over time, following the deformation and movements of the swimmers.
As the immersed boundary method, it accounts for the full, non-approximated description of the fluid dynamics.
%\review{Furthermore, when comparing this method to the CUTFEM method, in one instance, the high computational cost arises from projecting the swimmer onto the existing mesh, whereas in our case, the cost is associated with remeshing.}
This numerical method is very versatile and it has been used in a wide variety of contexts and physical problems, and it can be easily extended to cases in which the Newtonian fluid is substituted by a complex fluid, which is often the case of biological media.

@@

The velocity field $\Vel(t,x):]0,T]\times \CompDomain_t \rightarrow \R^d$ and the pressure field $\Pres(t,x):]0,T]\times\CompDomain_t \rightarrow \R$ satisfy the Navier-Stokes equations given by: 
\begin{equation}
	\begin{aligned}
		\rho_\Fluid \Big(\partial_t \Vel +( \Vel \cdot \nabla )\Vel \Big) \review{- \nabla \cdot \sigma(u,p)} &=  f%\nabla \cdot \Stress %\nabla \Pres + \Viscosity \Delta \Vel + f 
		\quad &\text{on $ ]0,T]\times \CompDomain_t$},
		\\
		\nabla \cdot \Vel &= 0  \quad&\text{on $ ]0,T]\times \CompDomain_t$},\\
		\Vel &= \bar{\Vel}^i% U + \Omega \times(x-\bar{x}) + u_d 
		\quad &\text{on $]0,T]\times \partial \Solid_t^i$},\\
		\Vel(0,x) &= \Vel_0(x) \quad &\text{on $ \{0\}\times\CompDomain_0$},\\
		\Vel(t,x) &= h(t,x) &\text{on $ ]0,T]\times\partial\CompDomain_{t,D}$},\\
		\sigma(u,p) \normal&=  g(t,x) &\text{on $ ]0,T]\times\partial\CompDomain_{t,N}$},
	\end{aligned}
	\label{Eq:NS}
\end{equation}
\review{where $\sigma(u,p)$ is the stress tensor $\sigma(u,p) = -\Pres\mathbb{I} + 2 \mu D(u)$, with $D(u) = \frac{1}{2}\left(\nabla u + (\nabla u)^T\right)$, and}
$\bar{\Vel}^i(t,x):[0,T]\times\partial \Solid_t^i \rightarrow \R^d$ results from the interaction between the fluid and the $i$-th swimmer's body and $f(t,x):[0,T]\times\CompDomain_t \rightarrow \R^d$ represents external volume forces. The function $u_0$ is the prescribed initial condition of the system. 
\begin{figure}
    \centering
\begin{center}
\begin{tikzpicture}

@@

In the case of swimming, $\bar{\Vel}^i$ can be split into two contributions. The first one is determined by the linear velocity $\tvel^i(t): [0,T]\to\R^d$ and angular velocity  $\angvel^i(t):[0,T]\to \R^{d^*}$ of the swimmer around its center of mass $\CenterMassi$, where $d^*=1$ if $d=2$ and $d^*=3$ if $d=3$.  \review{The second one is given by the deformation velocity $u_d^i$, defined on the boundary of the swimmer. This latter models the swimming gait for active particles and vanishes for rigid bodies.} The function $\bar{u}^i$ then becomes $\bar{\Vel}^i(t,x) = \tvel^i(t) + \angvel^i(t)\times (x-\CenterMassi)+ \Vel_d^i(t)$.

@@

Let us define the mass of the $i$-th swimmer by  \review{$\mass^i = \int_{\Solid^i} \Density_{\Solid}^i$, where $\Solid^i = \Solid^i_0$ is the reference configuration}, %, let $\CenterMassi = \frac{1}{\mass^i} \int_{\Solid^i} \Density_{\Solid}^i x$ be its center of mass, 
and $\Inertia^i = \int_{\Solid^i} \Density_{\Solid}^i (x-\CenterMassi) \otimes (x-\CenterMassi)$ 
its positive definite and symmetric inertia tensor. 
The Newton and Euler equations describing the rigid body velocities $\tvel^i$ and $\angvel^i$ read:
\begin{equation}
	\begin{aligned}
		\mass^i \frac{d}{dt}\tvel^i &= F_e^i -\int_{\partial \Solid^i} \sigma \normal \,\textrm{ds},\\
		\frac{d}{dt}(\Rmat \Inertia^i \Rmat^T \angvel^i) &= T_e^i -\int_{\partial \Solid^i} \sigma \times (x-\CenterMassi)\,\textrm{ds}, 
	\end{aligned}
	\label{Eq:RB}
\end{equation}

where $\normal$ is the unit outward normal to $\partial \Solid^i$. \review{Equations \eqref{Eq:RB} correspond to the balance of forces and torques applied to each swimmer, stating that non-zero net contributions from fluid stresses $\sigma n$ or additional external forces $F_e^i$ and torques $T_e^i$ lead to velocity variations.}

@@

In this subsection, we describe how a swimmer's collisions with solid obstacles, other swimmers ,as active particles, and the boundaries of the fluid domain are handled. Our model is based on a short-range contact-avoidance repulsive force introduced by R. Glowinski in \cite{glowinski}. \review{The force is activated in a collision zone of width $w_{col}$}.
%for which a collision zone of width $\rho$ is defined in which the forces are activated.
In equation \eqref{Eq:RB}, the external force and torque terms $F_e^i$ and $T_e^i$ summarize the physical interactions occurring when the distances $d_{ij}$ and $d_{i}$ between swimmer $i$ and another body $j$, or between swimmer $i$ and the domain boundary $\partial \Fluid_t$, are smaller than the width \review{$w_{col}$} of the collision zone.  
The definition of the collision force for a swimmer-swimmer or swimmer-boundary pair is given by:

@@

\review{
$$
F_{ij} = - \epsilon A  ( X_j - X_i)  1_{d_{ij} \leq w_{col}}, \qquad
F_{i \partial \Fluid_t} = - \epsilon' A ( X_{\partial \Fluid_t} - X_i )  1_{d_{i} \leq w_{col}}.
$$}

@@

\review{
$$
F_e^i = \sum_{(i,j)|d_{ij} \leq w_{col}} F_{ij} +  \sum_{i | d_i \leq w_{col}} F_{i \partial \Fluid_t},
$$
}
where the first sum runs over all the body pairs $(i,j)$ such that $d_{ij}\le w_{col}$, and the second sum runs over all body-boundary pairs such that $d_{i}\le w_{col}$.

\review{ Force $F_e^i$ leads to body rotations via its associated torque, defined by: 
$$
T_e^i = - (X_i - x_{CM}^i )\times F_e^i,
$$
where  $X_i$ is the contact point where $F_e^i$ is applied.}

@@

% discretisation ALE --- to rephrase & correct @LUCA
In the discrete setting, it is not guaranteed that displacing the mesh according to the solution of \eqref{Eq: VarFormALE} always produces a valid triangulation: large displacements could lead to element inversions.
In order to prevent these problems, mesh quality measures \cite{Field2000} are used to assess the validity of the triangulation: if the mesh deformation is ``small'' and the mesh quality remains above a predefined threshold, the domain is deformed according to the \ALE\ map; if the minimum of the mesh quality field falls below the threshold, the resulting mesh deformation is not viable and a remeshing procedure is applied before the \ALE\ map.

In our case, the discrete \ALE\ maps are computed by solving equation \eqref{Eq: VarFormALE} with piece-wise linear continuous finite elements. The spaces where the numerical solution and the test functions are chosen are defined as
\begin{equation}
	\begin{aligned}
		X_{\bar{\phi},h} &= \{  \phi , \phi \in [H^1(\CompDomain_{0})]^d\cap [\mathbb{P}_1(\CompDomain_{0})]^d, \phi=\bar{\phi} \text{ on $\partial \mathcal{S}_{0}$}\},\\
		X_{0,h} &= \{  \phi ,\phi \in [H^1_0(\CompDomain_{0})]^d\cap [\mathbb{P}_1(\CompDomain_{0})]^d\},
	\end{aligned}
\end{equation}
and the solution of the variational problem 
	\begin{equation}
		\begin{aligned}
			&\int_{\CompDomain_{0}} (1+\tau(X))\nabla \phi^{t_{n+1}}_h (X)  : \nabla v \,\dx= 0, \qquad &\text{$\forall v \in X_{0,h}$},
			\\
			&\mathcal{\phi}_h^{t_{n+1}}= \bar{\phi}^{t_{n+1}}, &\text{on $\partial\mathcal{S}_{0}$},
		\end{aligned}
  \label{eq:ALE_EDP}
	\end{equation}
\review{where $A:B = \sum_{i,j} A_{ij}B_{ij}$ the Frobenius inner product}, defines the new computational domain as $\CompDomain_{t_{n+1}}=\Alemap_h^{t_{n+1}}(\CompDomain_{0})$, where $\Alemap_h^{t_{n+1}}(X) = X + \phi_h^{t_{n+1}}(X)$.

In the latter equations \eqref{eq:ALE_EDP}, $\tau$ is a piecewise constant coefficient, defined on each element $e$ of the domain's discretization as $ \tau\big |_e=(1-V_{min}/V_{max})/(V_e/V_{max})$, where $V_{max}$, $V_{min}$  and $V_e$ are the volumes of the largest, smallest and current element of the domain discretization \cite{kanchi_3d_2007}. \review{This coefficient $\tau$ allows that the mesh deformation is  applied to elements of larger volume.}

\review{The evolution of the boundary of the swimmer is defined by both the rigid motion and its swimming gait by }

$$
\bar{\phi}^{t_{n+1}}(X) = \int_{0}^{t_{n+1}}\tvel + \angvel\times(X+\bar{\phi}^{t_n}(X)-X_{CM}- \phi^{t_n}(X_{CM})) + u_d(t,X)\, \mathrm{d}t
$$
\review{where $X_{CM}$ is the mass center of the swimmer in the reference domain at initial time $t=0$. In others words, the center of mass at the current time in the current domain is defined by $x_{CM} := X_{CM} + \phi(X_{CM})$.}

@@

\review{First, the rotation around the origin in the reference frame is performed, then the body is translated to its position in the current frame. } A few fixed point iterations are performed at each time step to ensure the convergence of the body's position.

@@

\color{blue}
\begin{eqnarray*}
\int_{\CompDomain_{t_{n+1}}} \rho_\Fluid \partial_t \Vel_h^{n+1}|_\Alemap  \cdot \tilde{\Vel} + \int_{\CompDomain_{t_{n+1}}} \rho_\Fluid ((\Vel_h^{n+1}-{\Vel_{\mathcal{A}}}_h^{n+1} )\cdot \nabla u_h^{n+1}) \cdot \tilde{\Vel}
 \\+ 2\mu \int_{\CompDomain_{t_{n+1}}} D(\Vel_h^{n+1}) : D( \tilde{\Vel}) -  \int_{\CompDomain_{t_{n+1}}} \Pres_h^{n+1} \nabla \cdot \tilde{\Vel} \\
 = \sum_{i=1}^N \int_{\partial \Solid_{t_{n+1}}^i} \sigma(\Vel_h^{n+1},\Pres_h^{n+1}) n \cdot \tilde{\Vel}
 + \int_{\CompDomain_{t_{n+1}}} f^{n+1} \cdot \tilde{\Vel},\\
 	\int_{\CompDomain_{t_{n+1}}} \tilde{\Pres} \nabla \cdot \Vel_h^{n+1} = 0,
  \end{eqnarray*}
  \begin{eqnarray*}
  \sum_{i=1}^N m^i \frac{d (\tvel^i)}{dt}^{n+1}\cdot \tilde{\tvel}^i = \sum_{i=1}^N \bigl[ F_e^i \cdot \tilde{\tvel}^i - \int_{\partial \Solid^i_{t_{n+1}}} \sigma \normal \cdot \tilde{\tvel}^i \bigr] ,
  \\ \sum_{i=1}^N \frac{d[R I^i R^T (\angvel^i)]^{n+1}}{dt} \cdot \tilde{\angvel}^i = \sum_{i=1}^N  \bigl[ T_e^i \cdot \tilde{\angvel}^i  -\int_{\partial \Solid^i_{t_{n+1}}} \sigma \times (x-\CenterMassi) \cdot  \tilde{\angvel}^i \bigr],
\label{Eq:discrete-var_form}
\end{eqnarray*}
for all $(\tilde{\Vel},\tilde{\Pres}) \in V_{h}^{t_{n+1}} \times Q_h^{t_{n+1}}, (\tilde{\tvel}^i,\tilde{\angvel}^i) \in \mathbb{R}^d\times \mathbb{R}^{d^*}$ for $i=1,\dots,N$.

@@

\bibliographystyle{}
\bibliography{}
\begin{thebibliography}{99.}

>>>>

\title*{Towards a computational framework using finite element methods with Arbitrary Lagrangian-Eulerian approach for swimmers with contact}
\titlerunning{A computational framework for swimmers}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Luca Berti, Laetitia Giraldi, Christophe Prud'homme, Céline Van Landeghem}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Luca Berti \at CNRS - Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg  \email{berti@math.unistra.fr}
\and Laetitia Giraldi \at Universit\'e C\^ote d'Azur, INRIA, CNRS, Calisto team, \email{laetitia.giraldi@inria.fr}
\and Christophe Prud'homme \at Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg - CNRS \email{christophe.prudhomme@math.unistra.fr}
\and Céline Van Landeghem \at Institut de Recherche Mathématique Avancée, UMR 7501 Université de Strasbourg - CNRS \email{c.vanlandeghem@unistra.fr}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract{Swimming involves a body's capability to navigate through a fluid by undergoing self-deformations. Typically, fluid dynamics are described by the Navier-Stokes equations, and when integrated with a swimming body, it results in a highly intricate model. This paper introduces a computational framework for simulating the movement of multiple swimmers with various geometries immersed in a Navier-Stokes fluid. The approach relies on the finite element method with an Arbitrary Lagrangian-Eulerian (ALE) framework to handle swimmer displacements. Numerous numerical experiments demonstrate the adaptability of the computational framework across various scenarios.
All the implementations are made using the \feelpp\ finite element library \cite{prudhomme_feelppfeelpp_2023}.}

@@

The problem of simulating the motion of deformable swimmers in a fluid can be addressed through various approaches, depending on the flow regime. In the low Reynolds number limit, when the viscous effects prevail over inertial effects, as it is the case for microscopic bodies in very viscous fluids \cite{huang_life_2013}, it is legitimate to consider that the fluid is governed by the Stokes equations \cite{happel_low_2012,lauga_hydrodynamics_2009}.

@@

In this case, the hydrodynamic drag can be simplified asymptotically by employing the Resistive Force Theory \cite{gray_propulsion_1955}, in which the hydrodynamic friction is related to the fluid velocity via an %prescribed 
anisotropic relation %operator 
depending on some parameters that account for the shape of the moving object. This approach does not require the numerical solution of the Stokes equations, but it has a
%Nevertheless, these approximations have 
very limited physical validity, often restricted to the case of very simple boundary-free domains.

%SBT
Slender body theory improves the Resistive Force Theory
to investigate the dynamics of slender particles in highly viscous flows \cite{cox_motion_1970, batchelor_slender-body_1970, keller_slender-body_1976,johnson_improved_1980}. 
This approach involves solving an integral equation which describes the effects of the fluid on the slender body. Assuming small deformations, the equilibrium of forces and torques can be expressed as a partial differential equation \cite{gadelha_counterbend_2013,  moreau_asymptotic_2018, el_khiyati_steering_2023}, whose solution defines the curve that describes the fiber. However, this method neglects the effects of fiber deformation on the fluid, leading to an approximation in accounting for the effects of the displacement of multiple swimmers.

%BEM (Lefebvre - Maury - Kenta)
A numerical method that is widely used in the micro-swimming community is the boundary element method, that relies on the integral formulation of the Stokes equations to determine the fluid velocity field \cite{pozrikidis_boundary_1992}. 
This formulation reduces the computational cost of the dynamics of the swimmer by working on the swimmer's boundary alone, which ensures significant memory savings since the fluid domain is not discretized. 
The boundary integral formulation expresses the fluid velocity at the boundary of the swimmer as a function of fluid stresses and velocities, via the fundamental solutions of the Stokes equations. Since these functions exhibit singular behaviour when the source and evaluation points are close together, a regularisation procedure needs to be employed for the numerical solution. Several solutions are possible: a regularisation of the numerical approximation of the singular integrals using a semi-analytic procedure \cite{huang_notes_1993} or the use of regularised kernels \cite{olson_coupling_2011}.

@@

% Méthode de frontière immergée
When inertial effects become more important and the low Reynolds number assumption is no longer valid, 
it is necessary to resort to the solution of the system coupling Navier-Stokes equations with Newton's equations for rigid bodies. 
A commonly used method involves approximating the values of fluid velocity and pressure on a fixed discretization of the domain and representing the swimmers using an implicit function that parameterizes their boundaries. 
These approaches are commonly referred to as Immersed Boundary Methods with level set functions describing the swimmer. 
The challenge of these methods lies in following the swimmer. 
For instance, one may use methods called CutFEM (Cut Finite Element Method), which project the swimmer's boundary onto the fixed mesh \cite{monasse_conservative_2012,bergmann_accurate_2014,bergmann_bioinspired_2016,hansbo_cut_2016,burman_cutfem_2015}.
%\review{However, this approach is computationally costly.}
%the CUTFEM approach in which mesh intersections are computationally costly.

@@

% Méthode FEM-ALE
In this chapter, we discuss an alternative method to compute the displacement of multiple deformable swimmers immersed in a Navier-Stokes fluid, which can be confined within a geometrically complex domain. This method is based on the finite element solution of the swimming problem, using the Arbitrary-Lagrangian-Eulerian description for the motion of the fluid domain.
This approach is popular in fluid-structure interaction problems \cite{chabannes_high-order_2013,pena_high_2012}, and it is based on a formulation of the fluid equations in an intermediate frame between the Eulerian and Lagrangian description.
A characteristic of this method is that the solutions are approximated on a mesh that deforms over time, following the deformation and movements of the swimmers.
As the immersed boundary method, it accounts for the full, non-approximated description of the fluid dynamics.
%\review{Furthermore, when comparing this method to the CUTFEM method, in one instance, the high computational cost arises from projecting the swimmer onto the existing mesh, whereas in our case, the cost is associated with remeshing.}
This numerical method is very versatile and it has been used in a wide variety of contexts and physical problems, and it can be easily extended to cases in which the Newtonian fluid is substituted by a complex fluid, which is often the case of biological media.

@@

The velocity field $\Vel(t,x):]0,T]\times \CompDomain_t \rightarrow \R^d$ and the pressure field $\Pres(t,x):]0,T]\times\CompDomain_t \rightarrow \R$ satisfy the Navier-Stokes equations given by: 
\begin{equation}
	\begin{aligned}
		\rho_\Fluid \Big(\partial_t \Vel +( \Vel \cdot \nabla )\Vel \Big) - \nabla \cdot \sigma(u,p) &=  f%\nabla \cdot \Stress %\nabla \Pres + \Viscosity \Delta \Vel + f 
		\quad &\text{on $ ]0,T]\times \CompDomain_t$},
		\\
		\nabla \cdot \Vel &= 0  \quad&\text{on $ ]0,T]\times \CompDomain_t$},\\
		\Vel &= \bar{\Vel}^i% U + \Omega \times(x-\bar{x}) + u_d 
		\quad &\text{on $]0,T]\times \partial \Solid_t^i$},\\
		\Vel(0,x) &= \Vel_0(x) \quad &\text{on $ \{0\}\times\CompDomain_0$},\\
		\Vel(t,x) &= h(t,x) &\text{on $ ]0,T]\times\partial\CompDomain_{t,D}$},\\
		\sigma(u,p) \normal&=  g(t,x) &\text{on $ ]0,T]\times\partial\CompDomain_{t,N}$},
	\end{aligned}
	\label{Eq:NS}
\end{equation}
where $\sigma(u,p)$ is the stress tensor $\sigma(u,p) = -\Pres\mathbb{I} + 2 \mu D(u)$, with $D(u) = \frac{1}{2}\left(\nabla u + (\nabla u)^T\right)$, and
$\bar{\Vel}^i(t,x):[0,T]\times\partial \Solid_t^i \rightarrow \R^d$ results from the interaction between the fluid and the $i$-th swimmer's body and $f(t,x):[0,T]\times\CompDomain_t \rightarrow \R^d$ represents external volume forces. The function $u_0$ is the prescribed initial condition of the system. 
\begin{figure}
    \centering
\begin{center}
\begin{tikzpicture}

@@

In the case of swimming, $\bar{\Vel}^i$ can be split into two contributions. The first one is determined by the linear velocity $\tvel^i(t): [0,T]\to\R^d$ and angular velocity  $\angvel^i(t):[0,T]\to \R^{d^*}$ of the swimmer around its center of mass $\CenterMassi$, where $d^*=1$ if $d=2$ and $d^*=3$ if $d=3$.  The second one is given by the deformation velocity $u_d^i$, defined on the boundary of the swimmer. This latter models the swimming gait for active particles and vanishes for rigid bodies. The function $\bar{u}^i$ then becomes $\bar{\Vel}^i(t,x) = \tvel^i(t) + \angvel^i(t)\times (x-\CenterMassi)+ \Vel_d^i(t)$.

@@

Let us define the mass of the $i$-th swimmer by  $\mass^i = \int_{\Solid^i} \Density_{\Solid}^i$, where $\Solid^i = \Solid^i_0$ is the reference configuration, %, let $\CenterMassi = \frac{1}{\mass^i} \int_{\Solid^i} \Density_{\Solid}^i x$ be its center of mass, 
and $\Inertia^i = \int_{\Solid^i} \Density_{\Solid}^i (x-\CenterMassi) \otimes (x-\CenterMassi)$ 
its positive definite and symmetric inertia tensor. 
The Newton and Euler equations describing the rigid body velocities $\tvel^i$ and $\angvel^i$ read:
\begin{equation}
	\begin{aligned}
		\mass^i \frac{d}{dt}\tvel^i &= F_e^i -\int_{\partial \Solid^i} \sigma \normal \,\textrm{ds},\\
		\frac{d}{dt}(\Rmat \Inertia^i \Rmat^T \angvel^i) &= T_e^i -\int_{\partial \Solid^i} \sigma \times (x-\CenterMassi)\,\textrm{ds}, 
	\end{aligned}
	\label{Eq:RB}
\end{equation}

where $\normal$ is the unit outward normal to $\partial \Solid^i$. Equations \eqref{Eq:RB} correspond to the balance of forces and torques applied to each swimmer, stating that non-zero net contributions from fluid stresses $\sigma n$ or additional external forces $F_e^i$ and torques $T_e^i$ lead to velocity variations.

@@

In this subsection, we describe how a swimmer's collisions with solid obstacles, other swimmers ,as active particles, and the boundaries of the fluid domain are handled. Our model is based on a short-range contact-avoidance repulsive force introduced by R. Glowinski in \cite{glowinski_fictitious_1998}. The force is activated in a collision zone of width $w_{col}$.
%for which a collision zone of width $\rho$ is defined in which the forces are activated.
In equation \eqref{Eq:RB}, the external force and torque terms $F_e^i$ and $T_e^i$ summarize the physical interactions occurring when the distances $d_{ij}$ and $d_{i}$ between swimmer $i$ and another body $j$, or between swimmer $i$ and the domain boundary $\partial \Fluid_t$, are smaller than the width $w_{col}$ of the collision zone.  
The definition of the collision force for a swimmer-swimmer or swimmer-boundary pair is given by:

@@

$$
F_{ij} = - \epsilon A  ( X_j - X_i)  1_{d_{ij} \leq w_{col}}, \qquad
F_{i \partial \Fluid_t} = - \epsilon' A ( X_{\partial \Fluid_t} - X_i )  1_{d_{i} \leq w_{col}}.
$$

@@

$$
F_e^i = \sum_{(i,j)|d_{ij} \leq w_{col}} F_{ij} +  \sum_{i | d_i \leq w_{col}} F_{i \partial \Fluid_t},
$$

where the first sum runs over all the body pairs $(i,j)$ such that $d_{ij}\le w_{col}$, and the second sum runs over all body-boundary pairs such that $d_{i}\le w_{col}$.

Force $F_e^i$ leads to body rotations via its associated torque, defined by: 
$$
T_e^i = - (X_i - x_{CM}^i )\times F_e^i,
$$
where  $X_i$ is the contact point where $F_e^i$ is applied.

@@

% discretisation ALE --- to rephrase & correct @LUCA
In the discrete setting, it is not guaranteed that displacing the mesh according to the solution of \eqref{Eq: VarFormALE} always produces a valid triangulation: large displacements could lead to element inversions.
In order to prevent these problems, mesh quality measures \cite{field_qualitative_2000} are used to assess the validity of the triangulation: if the mesh deformation is ``small'' and the mesh quality remains above a predefined threshold, the domain is deformed according to the \ALE\ map; if the minimum of the mesh quality field falls below the threshold, the resulting mesh deformation is not viable and a remeshing procedure is applied before the \ALE\ map.

In our case, the discrete \ALE\ maps are computed by solving equation \eqref{Eq: VarFormALE} with piece-wise linear continuous finite elements. The spaces where the numerical solution and the test functions are chosen are defined as
\begin{equation}
	\begin{aligned}
		X_{\bar{\phi},h} &= \{  \phi , \phi \in [H^1(\CompDomain_{0})]^d\cap [\mathbb{P}_1(\CompDomain_{0})]^d, \phi=\bar{\phi} \text{ on $\partial \mathcal{S}_{0}$}\},\\
		X_{0,h} &= \{  \phi ,\phi \in [H^1_0(\CompDomain_{0})]^d\cap [\mathbb{P}_1(\CompDomain_{0})]^d\},
	\end{aligned}
\end{equation}
and the solution of the variational problem 
	\begin{equation}
		\begin{aligned}
			&\int_{\CompDomain_{0}} (1+\tau(X))\nabla \phi^{t_{n+1}}_h (X)  : \nabla v \,\dx= 0, \qquad &\text{$\forall v \in X_{0,h}$},
			\\
			&\mathcal{\phi}_h^{t_{n+1}}= \bar{\phi}^{t_{n+1}}, &\text{on $\partial\mathcal{S}_{0}$},
		\end{aligned}
  \label{eq:ALE_EDP}
	\end{equation}
where $A:B = \sum_{i,j} A_{ij}B_{ij}$ the Frobenius inner product, defines the new computational domain as $\CompDomain_{t_{n+1}}=\Alemap_h^{t_{n+1}}(\CompDomain_{0})$, where $\Alemap_h^{t_{n+1}}(X) = X + \phi_h^{t_{n+1}}(X)$.

In the latter equations \eqref{eq:ALE_EDP}, $\tau$ is a piecewise constant coefficient, defined on each element $e$ of the domain's discretization as $ \tau\big |_e=(1-V_{min}/V_{max})/(V_e/V_{max})$, where $V_{max}$, $V_{min}$  and $V_e$ are the volumes of the largest, smallest and current element of the domain discretization \cite{kanchi_3d_2007}. This coefficient $\tau$ allows that the mesh deformation is  applied to elements of larger volume.

The evolution of the boundary of the swimmer is defined by both the rigid motion and its swimming gait by

$$
\bar{\phi}^{t_{n+1}}(X) = \int_{0}^{t_{n+1}}\tvel + \angvel\times(X+\bar{\phi}^{t_n}(X)-X_{CM}- \phi^{t_n}(X_{CM})) + u_d(t,X)\, \mathrm{d}t
$$
where $X_{CM}$ is the mass center of the swimmer in the reference domain at initial time $t=0$. In others words, the center of mass at the current time in the current domain is defined by $x_{CM} := X_{CM} + \phi(X_{CM})$.

@@

First, the rotation around the origin in the reference frame is performed, then the body is translated to its position in the current frame. A few fixed point iterations are performed at each time step to ensure the convergence of the body's position.

@@

\color{black}
\begin{eqnarray*}
\int_{\CompDomain_{t_{n+1}}} \rho_\Fluid \partial_t \Vel_h^{n+1}|_\Alemap  \cdot \tilde{\Vel} + \int_{\CompDomain_{t_{n+1}}} \rho_\Fluid ((\Vel_h^{n+1}-{\Vel_{\mathcal{A}}}_h^{n+1} )\cdot \nabla u_h^{n+1}) \cdot \tilde{\Vel}
 \\+ 2\mu \int_{\CompDomain_{t_{n+1}}} D(\Vel_h^{n+1}) : D( \tilde{\Vel}) -  \int_{\CompDomain_{t_{n+1}}} \Pres_h^{n+1} \nabla \cdot \tilde{\Vel} \\
 = \sum_{i=1}^N \int_{\partial \Solid_{t_{n+1}}^i} \sigma(\Vel_h^{n+1},\Pres_h^{n+1}) n \cdot \tilde{\Vel}
 + \int_{\CompDomain_{t_{n+1}}} f^{n+1} \cdot \tilde{\Vel},\\
 	\int_{\CompDomain_{t_{n+1}}} \tilde{\Pres} \nabla \cdot \Vel_h^{n+1} = 0,
  \end{eqnarray*}
  \begin{eqnarray*}
  \sum_{i=1}^N m^i \frac{d (\tvel^i)}{dt}^{n+1}\cdot \tilde{\tvel}^i = \sum_{i=1}^N \bigl[ F_e^i \cdot \tilde{\tvel}^i - \int_{\partial \Solid^i_{t_{n+1}}} \sigma \normal \cdot \tilde{\tvel}^i \bigr] ,
  \\ \sum_{i=1}^N \frac{d[R I^i R^T (\angvel^i)]^{n+1}}{dt} \cdot \tilde{\angvel}^i = \sum_{i=1}^N  \bigl[ T_e^i \cdot \tilde{\angvel}^i  -\int_{\partial \Solid^i_{t_{n+1}}} \sigma \times (x-\CenterMassi) \cdot  \tilde{\angvel}^i \bigr],
\label{Eq:discrete-var_form}
\end{eqnarray*}
for all $(\tilde{\Vel},\tilde{\Pres}) \in V_{h}^{t_{n+1}} \times Q_h^{t_{n+1}}, (\tilde{\tvel}^i,\tilde{\angvel}^i) \in \mathbb{R}^d\times \mathbb{R}^{d^*}$ for $i=1,\dots,N$.

@@

\bibliographystyle{plain}
\bibliography{references}

% \begin{thebibliography}{99.}
